---
title             : "Measurement Invariance of the Dirty Dozen: Student and Working Adult Samples"
shorttitle        : "Measurement Invariance"

author: 
  - name          : "Yang Yang"
    affiliation   : "1"
    corresponding : yes    # Define only one corresponding author
    address       : "Shanghai, China"
    email         : "yangyangsh@outlook.com"

  - name          : "John Kulas"
    affiliation   : "2"

affiliation:
  - id            : "1"
    institution   : "Roche"
  - id            : "2"
    institution   : "Montclair State University"

authornote: |
  Add complete departmental affiliations for each author here. Each new line herein must be indented, like this line.

  Enter author note here.

abstract: |
  One or two sentences providing a **basic introduction** to the field,  comprehensible to a scientist in any discipline.
  
  Two to three sentences of **more detailed background**, comprehensible  to scientists in related disciplines.
  
  One sentence clearly stating the **general problem** being addressed by  this particular study.
  
  One sentence summarizing the main result (with the words "**here we show**" or their equivalent).
  
  Two or three sentences explaining what the **main result** reveals in direct comparison to what was thought to be the case previously, or how the  main result adds to previous knowledge.
  
  One or two sentences to put the results into a more **general context**.
  
  Two or three sentences to provide a **broader perspective**, readily comprehensible to a scientist in any discipline.
  
  <!-- https://tinyurl.com/ybremelq -->
  
keywords          : "keywords"
wordcount         : "X"

bibliography      : ["r-references.bib", "measinvar.bib"]

floatsintext      : no
figurelist        : no
tablelist         : no
footnotelist      : no
linenumbers       : yes
mask              : no
draft             : no

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

```{r setup, include = FALSE}
library("papaja")
r_refs("r-references.bib")
```

```{r analysis-preferences}
# Seed for random number generation
set.seed(42)
knitr::opts_chunk$set(cache.extra = knitr::rand_seed, echo=FALSE, warning=FALSE, message=FALSE)
```



# Methods
We report how we determined our sample size, all data exclusions (if any), all manipulations, and all measures in the study. <!-- 21-word solution (Simmons, Nelson & Simonsohn, 2012; retrieved from http://ssrn.com/abstract=2160588) -->

```{r readingdata}

library(foreign)
library(careless)


masterdata <- read.spss("Dirty Dozon data for SIOP.sav")
DDdata <- data.frame(masterdata[c(1:3,34:45)])

table <- descr::freq(DDdata$selection, plot=FALSE)
dtable <- cbind(sample = rownames(table), table) ## to call out in paper


####################################### data screening below

careless_long <- longstring(DDdata[4:15])
careless_irv <- irv(DDdata[4:15])

careless_long <- data.frame(careless_long)
careless_irv  <- data.frame(careless_irv)

DDdata <- cbind(DDdata, careless_long, careless_irv)

#descr::freq(DDdata$careless_long)
#descr::freq(DDdata$careless_irv)

use <- DDdata[ which(DDdata$careless_long<7), ]


```

## Participants

In total `r nrow(DDdata)` individuals responded to the Dirty Dozen (as well as additional scales not the focus of the current presentation). This total was comprised of `r dtable[1,2]` `r dtable[1,1]`, `r dtable[2,2]` `r dtable[2,1]`, and `r dtable[3,2]` `r dtable[3,1]` individuals. After screening for undifferentiated responses via the `R` package `careless` [@R-careless], we retained `r nrow(use)` respondents who had no more than 6 undifferentiated similar responses across the 12 total items.

## Material

## Procedure

## Data analysis
We used `r cite_r("r-references.bib")` for all our analyses. 


# Results

```{r measinv}

## https://users.ugent.be/~yrosseel/lavaan/multiplegroup6Dec2012.pdf

library(lavaan)
library(semTools)

DD.model <-'mach   =~ A30 + A31 + A32 + A33
            narc   =~ A34 + A35 + A36 + A37
            psyc   =~ A38 + A39 + A40 + A41 '

measurementInvariance(model=DD.model, data=use, group="selection")

model1 <- cfa(model=DD.model, data=use, group="selection")
summary(model1, fit.measures=TRUE)
```

We looked at structural invariance as well as latent means [@steinmetz2009testing; @meredith1993measurement].

# Discussion


\newpage

# References

\begingroup
\setlength{\parindent}{-0.5in}
\setlength{\leftskip}{0.5in}

<div id="refs" custom-style="Bibliography"></div>
\endgroup
